---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covRflow

<!-- badges: start --> [![R-CMD-check](https://github.com/yasche/covRflow/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/yasche/covRflow/actions/workflows/R-CMD-check.yaml) <!-- badges: end -->

## Overview

covRflow allows you to retrieve the URLs of music cover artworks via an Application Programming Interface (API) (currently only 'Discogs') and display them in the Viewer pane of RStudio in an interactive cover flow-esque style. The package was a fun project for getting to know the 'httr2' package and the workings of the mysterious Viewer pane in RStudio.

## Installation

You can install the development version of covRflow from [GitHub](https://github.com/) with:

```{r, message=FALSE}
# install.packages("pak")
pak::pak("yasche/covRflow")
```

## Example

Workflow for retrieving the URLs of the cover artworks and displaying them in the Viewer pane. 

*Note:* You need a personal access token to access the 'Discogs' API. You can create one for free on the 'Discogs' [developer page](https://www.discogs.com/settings/developers).

```{r example, eval=FALSE}
library(covRflow)
example_albums |>
  create_request_discogs(access_token = "thisisasecret") |>
  retrieve_covers_discogs() |>
  covRflow()
```
